Portal Forecast

### 2018-12-10 evaluation.Rmd
Pull data from repo for website building

model_metadata = yaml::yaml.load_file("data/metadata.yaml")
pred_interval = model_metadata$pred_interval
models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
species_names = read.csv('PortalData/Rodents/Portal_rodent_species.csv',
                         stringsAsFactors=FALSE, na.strings = '') %>%
  dplyr::select(species = speciescode, full_species_name = scientificname) %>%
  dplyr::add_row(species='total', full_species_name='Total Rodents')

new_moons = read.csv('PortalData/Rodents/moon_dates.csv') %>%
            dplyr::mutate(censusdate = as.Date(censusdate))

# Setup rodent observations
species_abundance = portalr::abundance(clean=FALSE, shape='flat', level='treatment', 
                                       plots="longterm", time='newmoon') %>%
  dplyr::filter(treatment=="control") %>%
  dplyr::rename(actual = abundance, level = treatment) %>%
  dplyr::mutate(level='Controls',currency='abundance') %>%
  dplyr::filter(species %in% species_of_interest)

total_abundance = portalr::abundance(clean=FALSE, shape='flat', level='treatment', 
                                     plots="longterm", time='newmoon') %>%
  dplyr::filter(treatment=="control") %>%
  dplyr::group_by(newmoonnumber) %>%
  dplyr::summarise(actual=sum(abundance)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(level='Controls',currency='abundance',species='total')

>>>>

model_metadata = yaml::yaml.load_file('data/metadata.yaml')
pred_interval = model_metadata$pred_interval
models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/Portal_rodent_species.csv",
                          stringsAsFactors = F,na.strings = '') %>%
  dplyr::select(species = speciescode, full_species_name = scientificname) %>%
  dplyr::add_row(species='total', full_species_name='Total Rodents')

new_moons = read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv") %>%
            dplyr::mutate(censusdate = as.Date(censusdate))

# Setup rodent observations
species_abundance = portalr::abundance(path = "repo", clean=FALSE, shape='flat', level='treatment', 
                                       plots="longterm", time='newmoon') %>%
  dplyr::filter(treatment=="control") %>%
  dplyr::rename(actual = abundance, level = treatment) %>%
  dplyr::mutate(level='Controls',currency='abundance') %>%
  dplyr::filter(species %in% species_of_interest)

total_abundance = portalr::abundance(path = "repo", clean=FALSE, shape='flat', level='treatment', 
                                     plots="longterm", time='newmoon') %>%
  dplyr::filter(treatment=="control") %>%
  dplyr::group_by(newmoonnumber) %>%
  dplyr::summarise(actual=sum(abundance)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(level='Controls',currency='abundance',species='total')

### 2018-12-10 index.Rmd
Pull data from repo for website building

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance(clean=FALSE, level='treatment', plots="longterm") %>%
  dplyr::filter(treatment=="control")
obs_data$total = rowSums(dplyr::select(obs_data, -c(period, treatment)))
new_moons = read.csv('PortalData/Rodents/moon_dates.csv') %>%
                   dplyr::mutate(censusdate = as.Date(censusdate),
                          year = lubridate::year(newmoondate),
                          month = lubridate::month(newmoondate))

@@

# load in rodent species table to get scientific names to display on plots
species_table = read.csv('PortalData/Rodents/Portal_rodent_species.csv',
                          stringsAsFactors = F,na.strings = '')
most_abund_sp_names = dplyr::filter(species_table,speciescode %in% most_abund_sp$species) %>%      
                      dplyr::select(speciescode,scientificname)

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance(path = "repo", clean=FALSE, level='treatment', plots="longterm") %>%
  dplyr::filter(treatment=="control")
obs_data$total = rowSums(dplyr::select(obs_data, -c(period, treatment)))
new_moons = read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv") %>%
                   dplyr::mutate(censusdate = as.Date(censusdate),
                          year = lubridate::year(newmoondate),
                          month = lubridate::month(newmoondate))

@@

# load in rodent species table to get scientific names to display on plots
species_table = read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/Portal_rodent_species.csv",
                          stringsAsFactors = F,na.strings = '')
most_abund_sp_names = dplyr::filter(species_table,speciescode %in% most_abund_sp$species) %>%      
                      dplyr::select(speciescode,scientificname)
